Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

% Experimental setup: how we validated that we fixed the problem
To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code. Because not all clones can easily be automatically refactored, we define those that can. Using these definitions we can extract a sufficiently large set of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

% results: what have we learned by fixing the problem
We correlate the delta maintainability score with the factors that influence this score (clone volume, clone complexity, externally declared data used). We find that the biggest influencing factor is the volume of the clone. Our data shows that clones consisting of 63 or fewer tokens most often \textit{should not} be refactored. The other important factor is externally declared data that is used in the clone, clones with more than two externally declared variables most often do not improve maintainability when refactored.

>>>>

% Experimental setup: how we validated that we fixed the problem
To conduct such refactorings in a controlled environment, we create a tool that can automatically refactor a set of duplication problems in Java source code. Because not all clones can easily be automatically refactored, we define those that can. Using these definitions we can extract a sufficiently large set of refactored clones to perform our analyses. Our tool refactors 13k clones over 2k open-source Java projects and computes the delta maintainability scores.

% results: what have we learned by fixing the problem
We correlate the delta maintainability scores with the factors that influence this score (clone volume, clone complexity, externally declared data used). We find that the biggest influencing factor is the volume of the clone. Our data shows that clones consisting of 63 or fewer tokens most often \textit{should not} be refactored. The other important factor is externally declared data that is used in the clone, clones with more than two externally declared variables most often do not improve maintainability when refactored.
